### 2022-11-10 Paper.tex
Created document skeleton

\documentclass{report}

\begin{document}

\end{document}

### 2022-11-27 Paper.tex
the methods section's first iteration

@@
-\documentclass{report}
+\documentclass[]{report}
+\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
+\usepackage{graphicx,tabularx}%for figures and tables
+\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
+\usepackage[english]{babel}  %set the language to English
+\usepackage[margin=1.5in]{geometry} %change page margins 
+\usepackage{sectsty}%section headers
+\allsectionsfont{\sffamily\large}
+\subsectionfont{\sffamily\normalsize}
+\linespread{1.2}% line distance
+\usepackage{lipsum}% http://ctan.org/pkg/lipsum
+\usepackage{caption}%use for captions on tables
+%use this exact command.
+The style and bibliographystyle has to be authoryear (Havard).
+The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically.
+firstinits=true shortens the names: Albert Einstein -> A.
+Einstein
+\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
+\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
+\addbibresource{report.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
+\usepackage[compact]{titlesec}%include title formatting package
+
+% Title Page
+\title{Top Text}
+\author{Tom Jacobs and James Boogaard}
+\date{December 15th 2022 \\Module: SEAR \\Venlo, Limburg, Netherlands}
 
@@
 
+	\maketitle
+
+	\begin{abstract}
+		This is the abstract.
+
+		\pagenumbering{roman}
+
+	\end{abstract}
+
+	\tableofcontents
+	\setcounter{page}{3}
+	\listoffigures %UNCOMMENT IF YOU HAVE FIGURES
+	%\listoftables %UNCOMMENT IF YOU HAVE TABLES
+	\pagebreak
+
+	\pagenumbering{arabic}
+
+	\section{Introduction}
+	During the year there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image, which has led to many being made which on the one hand has given artist (a person that uses a text-to-image generator to create an image with text) many more options but has also made the landscape difficult to navigate.
+This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy so we can help give some perspective on which text-to-image generator is best for them.
+
+	Research paper was released on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations.
+We wanted to see which one out of the four we chose was the best for the artist according to specific criteria.
+
+	Our goal during the course of this reaserch paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.
+
+	The best text-to-image generator out of the four we chose will be stable diffusion.
+This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tume their result.
+Given enough time this will yield a more accurate result.
+
+	\section{Methods}
+
+	Our goal during the course of this research paper is to find out what the best text to image generator is, out of the four we chose, for artists who are experienced as well as artists who are not experienced in AI art generation.
+
+	A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.
+
+	This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose.
+Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
+The intervening variable in this case would be experience using these applications.
+
+	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition.
+We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
+With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
+this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
+Once the data is gathered, we can create a graph to compare the applications more easily.
+The people that carried out this experiment also consisted of one novice and one experienced individual.
+This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs.
+In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.
+
+	\section{Results}
+	\newpage	
+	\section{Discussion}
+
 \end{document}
+
+\printbibliography[title=References]
+
+\end{document}

### 2022-11-27 Paper.tex

@@
 	\section{Introduction}
-	During the year there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image, which has led to many being made which on the one hand has given artist (a person that uses a text-to-image generator to create an image with text) many more options but has also made the landscape difficult to navigate.
+	During the year of 2022 there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
+This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate.
+These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs.
 This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy so we can help give some perspective on which text-to-image generator is best for them.
 
-	Research paper was released on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations.
-We wanted to see which one out of the four we chose was the best for the artist according to specific criteria.
+	A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations.
+This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories.
+One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.
 

### 2022-11-28 Paper.tex
ccommit additions to the introduction

@@
 	\section{Introduction}
-	During the year of 2022 there has been a massive increase in the popularity of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
-This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate.
+During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
+This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate with its abundance of choice.
 These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs.
-This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy so we can help give some perspective on which text-to-image generator is best for them.
+This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.
 
@@
 
-	Our goal during the course of this reaserch paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.
+Our goal during the course of this research paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.
+
+Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation.
+The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.
+
+The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo.
+Stable diffusion was released in 2022 and makes use of the ai text-to-image synthesis technique known as latent diffusion.
+Midjourney which is currently in open beta and also makes use of latent diffusion to generate its images.
+DallE was released in January of 2021 and makes use of the V4 model to generate its images.
+Finally is dream by Wombo which was released in late 2021 and makes use of a combination of VOGAN and CLIP for text-to-image generation.
 
 The best text-to-image generator out of the four we chose will be stable diffusion.
-This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tume their result.
+This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tune their result.
 Given enough time this will yield a more accurate result.

### 2022-12-02 Paper.tex
Introduction extension

@@
 During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
-This has led to many different generators being made, which on the one hand has given artist, a person that uses a text-to-image generator to create an image with text, many more options but has also made the landscape difficult to navigate with its abundance of choice.
+This has led to many different generators being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image), but it has also made the landscape difficult to navigate with its abundance of choice.
 These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs.
@@
 One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.
+Another issue is that they don't allow average people to use their tools.
+Instead their results are created by the researchers themselves, this causes the results to show the absolute best a text-to-image generator can create instead of what the average artist can expect.
 
 Our goal during the course of this research paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.
+Our hope is that artists that are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.
 
@@
 
-The best text-to-image generator out of the four we chose will be stable diffusion.
-This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tune their result.
+We expect the best text-to-image generator out of the four we chose to be stable diffusion.
+This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result.
 Given enough time this will yield a more accurate result.
+This however, only applies for artists who are already experienced, we expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
+In the case of inexperienced artists, they might find DallE easier to use because it creates photo realistic results without having to fine tune any settings apart from their prompt.
 

### 2022-12-05 Paper.tex
Update introduction and methods

@@
 During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
-This has led to many different generators being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image), but it has also made the landscape difficult to navigate with its abundance of choice.
-These new options are great for the field as a whole, however it also means that artists who are not experienced may struggle to find the generator which suits their needs.
+You will likely have heard of at least one of these if you frequent the internet.
+This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists, (people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
 This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.
@@
 One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.
-Another issue is that they don't allow average people to use their tools.
-Instead their results are created by the researchers themselves, this causes the results to show the absolute best a text-to-image generator can create instead of what the average artist can expect.
+Another issue is that they don't allow average inexperienced artists to use their tools, instead their results are created by the researchers themselves.
+Because of this their results do not reflect what the average inexperienced artist can expect when using these text-to-image techniques.
 
-Our goal during the course of this research paper is to find out what is the best text-to-image generator, out of the four we chose, for artists who are experienced as well as artists who are not experienced in artificial art generation.
+Our goal during the course of this research paper is to find out what the best text-to-image generator is, out of the four we chose, in the case of an artist who is not experienced in the world of text-to-image generation.
 Our hope is that artists that are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.
 
-Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation.
+(?
+maybe instead focus on the tools inside the application.) Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation.
 The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.
@@
 Given enough time this will yield a more accurate result.
-This however, only applies for artists who are already experienced, we expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
-In the case of inexperienced artists, they might find DallE easier to use because it creates photo realistic results without having to fine tune any settings apart from their prompt.
+This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion.
+We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
+In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photorealistic results without having to fine tune any settings apart from the prompt.
 
@@
 
-	A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.
+	(?
+Instead look at amount of tools available) A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.
 
@@
 	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition.
-We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
-With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
-this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
+We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
+After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
+With those sets of data, we then run the images (each iteration) through an AI application developed by DeepAI that can give you a numerical value (distance) based on how close one image is to another, the lower the distance the closer the image.
+This way we can see how close each iteration is to the image we are trying to recreate.
+
 	Once the data is gathered, we can create a graph to compare the applications more easily.
@@
 This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs.
+
 	In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.

### 2022-12-06 Paper.tex
c

--- 2022-11-28 Paper.tex
@@
 The best text-to-image generator out of the four we chose will be stable diffusion.
-This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which allows the user more freedom to fine-tune their result.
+This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image) which, this allo user more freedom to fine-tune their result.
 Given enough time this will yield a more accurate result.
+This however, only applies for artists who are already experienced, we expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
+In the case of inexperienced artists, they might find DallE easier to use because it creates photo realistic results without having to fine tune any settings apart from their prompt.
 
@@
 Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
-The intervening variable in this case would be experience using these applications.
+The intervening variable in this case would be the amount of experience using these applications.
 
-	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition.
-We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (30 minutes ) and after each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
+	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition.
+We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
+After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application(each application will thus have their own history of the process of the participants tying to recreate the image).
 With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
@@
 The people that carried out this experiment also consisted of one novice and one experienced individual.
-This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs.
-In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.
+This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people).
+In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.
+
+	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
+These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
+The closer to zero the distance is, the closer the images are together.
+zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.
 
 	\section{Results}
+
 	\newpage
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=1\linewidth]{Bargraph}
+    	\caption{}
+    	\label{fig:bargraph}
+    \end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
+		\caption{}
+		\label{fig:linegraphstablediff}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphDall-E}
+		\caption{}
+		\label{fig:linegraphdall-e}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphDBW}
+		\caption{}
+		\label{fig:linegraphdbw}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphMidJ}
+		\caption{}
+		\label{fig:linegraphmidj}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{boxplotWithAllData}
+		\caption{}
+		\label{fig:boxplotwithalldata}
+	\end{figure}
+
 	\section{Discussion}

### 2022-12-06 Paper.tex

--- 2022-12-05 Paper.tex
@@
 Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
-The intervening variable in this case would be experience using these applications.
+The intervening variable in this case would be the amount of experience using these applications.
+
+	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition.
+We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
+After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application(each application will thus have their own history of the process of the participants tying to recreate the image).
+With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
+this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
+Once the data is gathered, we can create a graph to compare the applications more easily.
+The people that carried out this experiment also consisted of one novice and one experienced individual.
+This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people).
+In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.
+
+	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
+These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
+The closer to zero the distance is, the closer the images are together.
+zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.
 
@@
 	\section{Results}
+
 	\newpage
+    \begin{figure}
+    	\centering
+    	\includegraphics[width=1\linewidth]{Bargraph}
+    	\caption{}
+    	\label{fig:bargraph}
+    \end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
+		\caption{}
+		\label{fig:linegraphstablediff}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphDall-E}
+		\caption{}
+		\label{fig:linegraphdall-e}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphDBW}
+		\caption{}
+		\label{fig:linegraphdbw}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{LineGraphMidJ}
+		\caption{}
+		\label{fig:linegraphmidj}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=1\linewidth]{boxplotWithAllData}
+		\caption{}
+		\label{fig:boxplotwithalldata}
+	\end{figure}
+
 	\section{Discussion}

### 2022-12-10 Paper.tex
commit (update of graphs with keys)
updating the data with new dalle info from tom
Extended introduction
Added trends graph
Updated secondary research question

@@
 
-(?
-maybe instead focus on the tools inside the application.) Another question we take a look at is to find the best technique out of the four applications that we use and then analysing why that technique is so effective for artificial intelligence text-to-image generation.
-The techniques we will take a look at are latent diffusion, the V4 model, and VOGAN and CLIP.
+Another question we take a look at is which applications have access to the most tools.
+More tools allow the artist more freedom to improve their results in a multitude of ways.
+Take for example inpainting, both Dall-E and stable diffusion give the artist access to this.
+With inpainting you can select, or paint over, a part of an image, you can then tell the generator what you would like to have generated in the selected area.
+More tools may sound great, however in practice inexperienced artists may struggle to get the hang of these kinds of tools.
+
+\pagebreak
 
 The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo.
-Stable diffusion was released in 2022 and makes use of the ai text-to-image synthesis technique known as latent diffusion.
-Midjourney which is currently in open beta and also makes use of latent diffusion to generate its images.
-DallE was released in January of 2021 and makes use of the V4 model to generate its images.
-Finally is dream by Wombo which was released in late 2021 and makes use of a combination of VOGAN and CLIP for text-to-image generation.
+We came to these models after looking at several applications in google trends.
+This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
+You may notice below in Figure 1 that Dream by Wombo is not that popular anymore, however it was one of the first openly accessible text-to-image applications out there
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=1\linewidth]{TrendsPlotWithLegend}
+	\caption{Results from Google Trends showing the popularity of different text-to-image applications}
+	\label{fig:TrendsPlotWithLegend}
+\end{figure}
 
@@
 
-	(?
-Instead look at amount of tools available) A secondary research question that we take a look at in this paper is to find out the strengths of the different ai text to image generation techniques used in the applications we have chosen.
+	In order to find out which is the best one, we will look at two things, namely: their accuracy in recreating an image, and their ease of use for inexperienced artists.
 
-	This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose.
+	(?) This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose.
 Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
@@
 We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
-After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application(each application will thus have their own history of the process of the participants tying to recreate the image).
+After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image).
 With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
@@
 	\newpage
-    \begin{figure}
-    	\centering
-    	\includegraphics[width=1\linewidth]{Bargraph}
-    	\caption{}
-    	\label{fig:bargraph}
-    \end{figure}
 
@@
 		\label{fig:linegraphstablediff}
+	\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1\linewidth]{Bargraph}
+	\caption{}
+	\label{fig:bargraph}
 \end{figure}

### 2022-12-11 Paper.tex
Added subsections

@@
 	\section{Introduction}
+
+	\subsection{Context and background}
 During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
@@
 
-Our goal during the course of this research paper is to find out what the best text-to-image generator is, out of the four we chose, in the case of an artist who is not experienced in the world of text-to-image generation.
-Our hope is that artists that are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.
+	\subsection{Problem and hypothesis}
+Our goal during the course of this research paper is to find out what the best text-to-image generator is out of the four we chose, in the case of an artist who is not experienced in the world of text-to-image generation.
+Our hope is that artists who are new to text-to-image generation will be able to make an educated decision on which generator is best for them on the basis of this paper.
 
@@
 
-\pagebreak
-
 The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo.
@@
 This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
-You may notice below in Figure 1 that Dream by Wombo is not that popular anymore, however it was one of the first openly accessible text-to-image applications out there
+You may notice below in Figure 1 that Dream by Wombo is not that popular anymore, however it was one of the first openly accessible text-to-image applications out there.
 
@@
 
+\pagebreak
+
 	\section{Methods}
 
+	\subsection{Data collection}
 	Our goal during the course of this research paper is to find out what the best text to image generator is, out of the four we chose, for artists who are experienced as well as artists who are not experienced in AI art generation.
@@
 
-	(?) This paper is used as an attempt to prove that stable diffusion is the best application out of the four, we chose.
 	Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
@@
 
+	\subsubsection{Generating images}
 	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition.
@@
 After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image).
-With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
+
+	\subsubsection{Scoring generated images}
+	With those sets of data, we then plug the images (each iteration) into an AI application, developed by DeepAI, that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
 this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
-Once the data is gathered, we can create a graph to compare the applications more easily.
-The people that carried out this experiment also consisted of one novice and one experienced individual.
-This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people).
-In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.
 
 	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
-These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
+These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
 The closer to zero the distance is, the closer the images are together.
@@
 
-	We have chosen an image that we find sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections and complex composition.
+	When choosing an image to compare each result to, we chose one that sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections, complex composition, lighting differences and multiple objects within the image.
 We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
 After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
-With those sets of data, we then run the images (each iteration) through an AI application developed by DeepAI that can give you a numerical value (distance) based on how close one image is to another, the lower the distance the closer the image.
-This way we can see how close each iteration is to the image we are trying to recreate.
+
+	\subsection{Visualizing data}
 
@@
 	In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.
+
+	\pagebreak
 

### 2022-12-11 Paper.tex
commit

--- 2022-12-10 Paper.tex
@@
 \usepackage[compact]{titlesec}%include title formatting package
+\usepackage[section]{placeins}
+\usepackage{placeins}
 
@@
 We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
-In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photorealistic results without having to fine tune any settings apart from the prompt.
+In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photo-realistic results without having to fine tune any settings apart from the prompt.
 
@@
 	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
-These fators are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
+These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
 The closer to zero the distance is, the closer the images are together.
@@
 
+	\pagebreak
 	\section{Results}
 
-	\newpage
-
-	\begin{figure}
+	\begin{figure}[!!htbp]
 		\centering
@@
 
-\begin{figure}
+\begin{figure}[!htbp]
 	\centering
-	\includegraphics[width=1\linewidth]{Bargraph}
+	\includegraphics[width=1\linewidth]{LineGraphMidJ}
 	\caption{}
-	\label{fig:bargraph}
+	\label{fig:linegraphmidj}
 \end{figure}
 
-	\begin{figure}
+\subsection{figure 2 and 3}
+
+What is interesting in both figure one and two is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
+This is seen with Subject two having nearly double the amount of iterations when compared to Subject one in figure one and then Subject 1 having more iterations than Subject two in figure two.
+Another point of interest is that the application in figure one has as a small amount of iterations when compared to the other applications.
+(-make reference to the fact that subject 2 has a bit of exper with sd and subject 1 has expr with midJ-).
+
+\begin{figure}[!htbp]
 	\centering
@@
 
-	\begin{figure}
+\begin{figure}[!htbp]
 	\centering
@@
 \end{figure}
+\subsection{figure 4 and 5}
 
-	\begin{figure}
+In figure two we see it has the most iterations out of any of the other applications.
+The spread of the distances is also the largest out of any of the other applications.
+When comparing the amount of iterations that each subject has in both figure on and figure two, these two applications are very close.(-This can be attributed to the fact that the amount of experience with these graphs is very similar for both subjects-)
+
+\begin{figure}[!htbp]
 	\centering
-		\includegraphics[width=1\linewidth]{LineGraphMidJ}
+	\includegraphics[width=1\linewidth]{Bargraph}
 	\caption{}
-		\label{fig:linegraphmidj}
+	\label{fig:bargraph}
 \end{figure}
+\subsection{figure 6}
+Figure 5 shows that the average distances of all the applications from broth subjects one and two are very close.(this is due to the random nature of t-i-g and shows that a good application is more judged by the functionality it offers rather than its algorithm when it comes to new comers).
+When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.
 
-	\begin{figure}
+	\begin{figure}[!htbp]
 		\centering
@@
 	\end{figure}
+\subsection{figure 7}
 
+	In Figure 6 there are two important points of interest.
+Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between q2 and q3.
+Second is that Stable Diffusion has the largest median distance.
+Mention something about the outliers.
+
+	\pagebreak
 	\section{Discussion}
+	\subsection{Title}
+
+	During the course of this research we were able to prove the legitimacy of our secondary research question.
+This was done by a analysing figures two through to six.
+The applications shown in figure two and three are applications that both subjects have experience in(Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion).
+What makes figure two and three important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate.
+
+	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
+using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.
+
+	When we take a look at figure six we can see that even though even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars in very small.
+This can be attributed to the nature of text-to-image generation being that of a random series of attempt until the user reaches a point where they are happy with the picture.
+This is further proven when you look at any of the patterns for figures 2 through 5 and how the distance for each iterations follows no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
+
+	\subsection{Secondary research question justification}
+
+	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications.
+What we do know is that if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make the faster you are more likely to get the result you are looking for.
 

### 2022-12-11 Paper.tex

@@
 After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image).
-With those sets of data, we then plug the images (each iteration) into an AI application that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
+
+	\subsubsection{Scoring generated images}
+	With those sets of data, we then plug the images (each iteration) into an AI application, developed by DeepAI, that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
 this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
-Once the data is gathered, we can create a graph to compare the applications more easily.
-The people that carried out this experiment also consisted of one novice and one experienced individual.
-This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs(one graph for each group of people).
-In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of the ai generation applications use, we can notice if there is a pattern of success or failure with each and thus are able to compare them and see which one is the best.
 
@@
 	\pagebreak
+
 	\section{Results}
+
+	\newpage
 

### 2022-12-12 Paper.tex
Fixed subsubsections
Rewrote secondary rq

@@
 Einstein
+\setcounter{secnumdepth}{3}
+\setcounter{tocdepth}{3}
 \usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
@@
 \usepackage{placeins}
+\titleformat*{\subsubsection}{\normalsize\bfseries}
 
@@
 One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.
-Another issue is that they don't allow average inexperienced artists to use their tools, instead their results are created by the researchers themselves.
-Because of this their results do not reflect what the average inexperienced artist can expect when using these text-to-image techniques.
 
@@
 
-Another question we take a look at is which applications have access to the most tools.
-More tools allow the artist more freedom to improve their results in a multitude of ways.
-Take for example inpainting, both Dall-E and stable diffusion give the artist access to this.
-With inpainting you can select, or paint over, a part of an image, you can then tell the generator what you would like to have generated in the selected area.
-More tools may sound great, however in practice inexperienced artists may struggle to get the hang of these kinds of tools.
+Another question we take a look at is what makes an application good for an inexperienced artist.
+In answering this question we will consider: the tools available to an artist, the difficulty in using these tools, the accuracy in generating images, the learning curve of an application and the speed with which the application can generate images.
+With these points of consideration it should be possible to score each application on their ease of use, and on their future potential if the artist were to stick with that application.
 
@@
 
-\begin{figure}[!htb]
+\begin{figure}[!h]
 	\centering
@@
 
+\par\bigskip
+
 We expect the best text-to-image generator out of the four we chose to be stable diffusion.
@@
 We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
-In the case of a completely inexperienced artist, they might find Dall-E easier to use because it can create photo-realistic results without having to fine tune any settings apart from the prompt.
+In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.
 
@@
 
-	In order to find out which is the best one, we will look at two things, namely: their accuracy in recreating an image, and their ease of use for inexperienced artists.
-
-	Our x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
-The intervening variable in this case would be the amount of experience using these applications.
+	In order to find out which is the best one, we will first look at the accuracy with which the generator can create images.
+We will score the accuracy with an API developed by DeepAI which can calculate image similarity.
 
@@
 
-	In terms of our secondary research question this method also gives us insight if we are aware of the techniques each of them use we can notice if there is a pattern of success or failure with each.
+	In these graphs the x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
+The intervening variable in this case would be the amount of experience using these applications.
 
@@
 	\section{Results}
-
-	\newpage
 

### 2022-12-12 Paper.tex
commit

@@
 \end{figure}
+
+\pagebreak
 \subsection{figure 4 and 5}
@@
 \end{figure}
+\pagebreak
 \subsection{figure 6}
@@
 	\end{figure}
+\pagebreak
 \subsection{figure 7}
@@
 	\section{Discussion}
-	\subsection{Title}
+
+	\subsection{Interpretation of figures 2 and 3}
 
@@
 
+	\subsection{Interpretation of figures 3 and 4}
+
 	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
 using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.
+
+	\subsection{Interpretation of figures 5 and 6}
 
@@
 
+	In order to answer the secondary research question looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of an of generated images with inexperienced users which makes sense as they may struggle to use said functionality.
+This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.
 With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications.
 What we do know is that if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make the faster you are more likely to get the result you are looking for.
+
+	\subsection{Answering primary research question}
+
+	Our primary research question can then be answered now that we know what makes a good ai text-to-image application and that is how fast the application is able to generate iterations.
+With this in mind we can then say that Dall-E has the most iterations.
+It also offers a very streamline user experience and is easy to access and intuitive to use.
+
+	\subsection{Further research}
+
+	The ways in which our research can be carried out in an improved manner are to firstly use a bigger sample size in order make the results of the research more convincing.
+This can be done by using more text-to-image applications and trying to recreate more than just one picture.
+
+	Secondly you can use many different ways to compare images rather than just one in order to make the results more accurate.
+This can be done with surveys where you ask people which image is closer to a humans perspective or by using not just one application for image comparison.
 

### 2022-12-12 Paper.tex
commit

@@
 You will likely have heard of at least one of these if you frequent the internet.
-This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists, (people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
-This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process so we can help people gain some perspective on which text-to-image generator is best for their needs.
+This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists(people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
+This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process.
+This allows us to help people gain some perspective on which text-to-image generator is best for their needs.
 
@@
 
-\par\bigskip
+\pagebreak
 
@@
 Given enough time this will yield a more accurate result.
-This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion.
-We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
-In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.
 
@@
 	\subsection{Data collection}
-	Our goal during the course of this research paper is to find out what the best text to image generator is, out of the four we chose, for artists who are experienced as well as artists who are not experienced in AI art generation.
+	Our goal during the course of this research paper is to find out what the best text to image generator is, out of the four we chose, for artists who are inexperienced in AI art generation.
 
@@
 	\subsubsection{Generating images}
-	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition.
-We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
-After each iteration we take the generated image (iteration) and add it to a list of the iterations that we created while recreating that image for that specific application (each application will thus have their own history of the process of the participants tying to recreate the image).
+
+	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition(see figure 2 below).
+	Subject 1 has experience with Midjourney and Subject 2 has experience with Stable diffusion and neither of them have any experience in the other applications.
+Both Subject 1 and Subject 2 then use each of the four text-to-image generation applications to try and recreate that image within a given time frame (15 minutes per application).
+After each iteration we take the generated image and add it to a list of the iterations for that application.
+
+	\begin{figure}[!h]
+		\centering
+		\includegraphics[width=1\linewidth]{OG}
+		\caption{}
+		\label{fig:og}
+	\end{figure}
 
 	\subsubsection{Scoring generated images}
-	With those sets of data, we then plug the images (each iteration) into an AI application, developed by DeepAI, that can give you a numerical value for how close one image is to another and see how close each iteration is to the image we are trying to recreate.
-this then gives us insight into how fast the application is (how efficient its technique is) and how many iterations you have to do to achieve a certain result.
+	With those sets of data, we then plug the images (each iteration) into the image similarity checking API, developed by DeepAI, that can give you a numerical value for how close one image is to another.
+This way we can see how close each iteration is to the image we are trying to recreate.
+The amount of iterations each application is able to create then gives us insight into how fast the application is and how many iterations you have to do to achieve a certain result.
+We also gain an idea of how easy to use each application is through this process.
 
 	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
-These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing program's unit of measurement (the unit is called distance.
+These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing API's unit of measurement (the unit is called distance.
 The closer to zero the distance is, the closer the images are together.
-zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.
-
-	When choosing an image to compare each result to, we chose one that sufficiently covers all the hard parts of recreating an image using ai art generation such as reflections, complex composition, lighting differences and multiple objects within the image.
-We then use each of the four artificial intelligence applications to try and recreate that image within a given time frame (15 minutes).
-After each iteration we take that image and compile it into a list of the iterations for the process of recreating that image for that specific application.
+Zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.
 
@@
 
-	Once the data is gathered, we can create a graph to compare the applications more easily.
-The people that carried out this experiment also consisted of one novice and one experienced individual.
-This is to see which is the best application for each group of people and thus, the results will be conveyed on two separate graphs.
+	Once the data is gathered, we can create graphs to compare the applications more easily.
 
@@
 The intervening variable in this case would be the amount of experience using these applications.
+
+	We also want to check each applications average result across both Subject 1 and Subject 2 in order to compare how close each iteration gets to the original image on average.
+This will show us if there are any large differences between the applications as a whole.
+If there is this will play a role in choosing which is the best application.
+
+	The last set of important data we want to visually represent is the min and max of each application and how far spread the results of each application are in order to see how reliable each application is.
 
@@
 
-\subsection{figure 2 and 3}
+\subsection{Figure 3 and 4}
 
 What is interesting in both figure one and two is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
-This is seen with Subject two having nearly double the amount of iterations when compared to Subject one in figure one and then Subject 1 having more iterations than Subject two in figure two.
+This is seen with Subject two having nearly double the amount of iterations when compared to Subject one in figure 3 and then Subject 1 having more iterations than Subject two in figure 4.
 Another point of interest is that the application in figure one has as a small amount of iterations when compared to the other applications.
-(-make reference to the fact that subject 2 has a bit of exper with sd and subject 1 has expr with midJ-).
-
 \begin{figure}[!htbp]
@@
 \pagebreak
-\subsection{figure 4 and 5}
+\subsection{Figure 5 and 6}
 
-In figure two we see it has the most iterations out of any of the other applications.
-The spread of the distances is also the largest out of any of the other applications.
+In figure 5 we see it has the most iterations out of any of the other applications.
 When comparing the amount of iterations that each subject has in both figure on and figure two, these two applications are very close.(-This can be attributed to the fact that the amount of experience with these graphs is very similar for both subjects-)
@@
 \pagebreak
-\subsection{figure 6}
+\subsection{Figure 7}
 Figure 5 shows that the average distances of all the applications from broth subjects one and two are very close.(this is due to the random nature of t-i-g and shows that a good application is more judged by the functionality it offers rather than its algorithm when it comes to new comers).
@@
 \pagebreak
-\subsection{figure 7}
+\subsection{Figure 8}
 
-	In Figure 6 there are two important points of interest.
+	In Figure 8 there are two important points of interest.
 Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between q2 and q3.
+This means the spread of the distances is also the largest out of any of the other applications.
 Second is that Stable Diffusion has the largest median distance.
@@
 
-	\subsection{Interpretation of figures 2 and 3}
+	\subsection{Interpretation}
 
@@
 
-	\subsection{Interpretation of figures 3 and 4}
-
 	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
 using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.
-
-	\subsection{Interpretation of figures 5 and 6}
 
@@
 
-	In order to answer the secondary research question looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of an of generated images with inexperienced users which makes sense as they may struggle to use said functionality.
+	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of an of generated images with inexperienced users which makes sense as they may struggle to use said functionality(!
+add section on ease of use Stable diffusion we looking at you -This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion.
+We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
+In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.-).
 This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.
+
 	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications.

### 2022-12-12 Paper.tex
Wrote abstract

@@
 	\begin{abstract}
-		This is the abstract.
+		Following the explosion of artificial intelligence during the year of 2022, there now are many text-to-image generation applications out there.
+This is great for the field of artificial intelligence as a whole, however it has made knowing which application is best quite hard for artists who are new to text-to-image generation.
+This paper looks at four of the most popular generators, with the aim to find out which one is the best for an inexperienced artist.
 

### 2022-12-13 Paper.tex
commit

@@
 
-In figure 5 we see it has the most iterations out of any of the other applications.
-When comparing the amount of iterations that each subject has in both figure on and figure two, these two applications are very close.(-This can be attributed to the fact that the amount of experience with these graphs is very similar for both subjects-)
+In figure 5 we see that Dall-E has the most iterations out of any of the other applications.
+When comparing the amount of iterations that each subject has in both figure 3 for Stable diffusion and figure 4 for Midjourney, the two applications are very far apart.
+In contrast the amount of iterations between each subject is very close together in figure 5 for Dall-E and figure 6 for Dream by Wombo.
 
@@
 \subsection{Figure 7}
-Figure 5 shows that the average distances of all the applications from broth subjects one and two are very close.(this is due to the random nature of t-i-g and shows that a good application is more judged by the functionality it offers rather than its algorithm when it comes to new comers).
+Figure 5 shows that the average distances of all the applications from both subjects one and two are very close.
 When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.
@@
 	In Figure 8 there are two important points of interest.
-Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between q2 and q3.
+Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between quartile 2 and quartile 3.
 This means the spread of the distances is also the largest out of any of the other applications.
 Second is that Stable Diffusion has the largest median distance.
-Mention something about the outliers.
 
@@
 
-	During the course of this research we were able to prove the legitimacy of our secondary research question.
-This was done by a analysing figures two through to six.
-The applications shown in figure two and three are applications that both subjects have experience in(Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion).
-What makes figure two and three important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate.
+	In order to find the best application out of the four we chose we needed to see what actually makes a text-to-image generation application good.
+This was done by a analysing figures 3 through to 7.
+The applications shown in figure 3 and 4 are applications that both subjects have experience in (Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion).
+What makes figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate because the quality of the images is very random which can be seen with how the line graphs from figures 3 to 6 all fluctuate hugely and never set any kind of discernible pattern.
 
-	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
-using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.
+	In figure 5 and 6 we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
+using comparative analysis we can then compare both the graphs that the users have experience in (being figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.
 
-	When we take a look at figure six we can see that even though even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars in very small.
-This can be attributed to the nature of text-to-image generation being that of a random series of attempt until the user reaches a point where they are happy with the picture.
-This is further proven when you look at any of the patterns for figures 2 through 5 and how the distance for each iterations follows no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
+	When we take a look at figure 7 we can see that even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars is very small.
+This can be attributed to the nature of text-to-image generation being that of a random series of attempts until the user reaches a point where they are happy with the result.
+This is further proven when you look at any of the patterns for figures 3 through 6 and how the distance for each application's iterations follow no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
+An example of this can be seen in figure 4 with Subject 1.
 
-	\subsection{Secondary research question justification}
+	\subsection{Answering secondary research question}
 
-	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of an of generated images with inexperienced users which makes sense as they may struggle to use said functionality(!
-add section on ease of use Stable diffusion we looking at you -This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion.
-We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get.
-In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.-).
-This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.
+	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of generated images with inexperienced users which makes sense as they may struggle to use said functionality.This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.
+	We also looked at how easy the application was to gain access to and came to the conclusion that every one of them was very easy to use and gain access to, so that also became an irrelevant comparison factor.
 
-	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications.
-What we do know is that if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make the faster you are more likely to get the result you are looking for.
+	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generation technique is nor is it about how much functionality it supplies it's user.
+This is because AI text-to-image generation is very random and relies a lot on luck with our current technology even for users that are experienced with these applications.
+What we do know is that currently if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make, the faster you are more likely to get the result you are looking for.
 
@@
 
-	Our primary research question can then be answered now that we know what makes a good ai text-to-image application and that is how fast the application is able to generate iterations.
-With this in mind we can then say that Dall-E has the most iterations.
-It also offers a very streamline user experience and is easy to access and intuitive to use.
+	Our primary research question can then be answered now that we know what makes an AI text-to-image application good for an inexperienced user and that is how fast the application is able to generate iterations.
+With this in mind we can then say that the best application out of the four we chose is Dall-E as it is able to generate the most iterations.
+On a side note our experience with it also lead to us believing that it offers a very streamline user experience, is easy to access and intuitive to use.
 

### 2022-12-14 Paper.tex
Added references

@@
 
-A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis" that makes use of surveys to compare models for text-to-image generations.
+A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis", \cite{agnese2020survey} that makes use of surveys to compare models for text-to-image generations.
 This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories.
@@
 The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo.
-We came to these models after looking at several applications in google trends.
-This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
+We came to these models after looking at several applications in Google Trends.
+\cite{googleTrends} This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
 You may notice below in Figure 1 that Dream by Wombo is not that popular anymore, however it was one of the first openly accessible text-to-image applications out there.
@@
 We will score the accuracy with an API developed by DeepAI which can calculate image similarity.
+\cite{imageSimilarity}
 
@@
 	\subsubsection{Scoring generated images}
-	With those sets of data, we then plug the images (each iteration) into the image similarity checking API, developed by DeepAI, that can give you a numerical value for how close one image is to another.
+	With those sets of data, we then plug the images (each iteration) into the image similarity checking API, \cite{imageSimilarity}, that can give you a numerical value for how close one image is to another.
 This way we can see how close each iteration is to the image we are trying to recreate.
@@
 
-\end{document}
-
+\newpage
 \printbibliography[title=References]

### 2022-12-14 Paper.tex
Cropped result graphs
Increased spacing between sections
commit

@@
 \titleformat*{\subsubsection}{\normalsize\bfseries}
+\titlespacing{\subsection}{0pt}{15pt}{0pt}
+\titlespacing{\subsubsection}{0pt}{10pt}{0pt}
 
 % Title Page
-\title{Top Text}
+\title{A comparison of the most popular AI text-to-image generation applications}
 \author{Tom Jacobs and James Boogaard}
@@
 	\begin{abstract}
-		Following the explosion of artificial intelligence during the year of 2022, there now are many text-to-image generation applications out there.
+		Following the explosion of artificial intelligence during the year of 2022, there are now many text-to-image generation applications out there.
 This is great for the field of artificial intelligence as a whole, however it has made knowing which application is best quite hard for artists who are new to text-to-image generation.
@@
 You will likely have heard of at least one of these if you frequent the internet.
-This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists(people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
+This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
 This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process.
@@
 This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories.
-One issue with this paper was that is was written before the explosion of consumer text-to-image generators happened, which is why we will instead focus on modern consumer-grade generators which are available today.
+One issue with this paper was that it was written before the explosion of consumer text-to-image generators happened in 2022, which is why we will instead focus on modern consumer-grade generators which are available today.
 
@@
 	Another question we take a look at is what makes an application good for an inexperienced artist.
-In answering this question we will consider: the tools available to an artist, the difficulty in using these tools, the accuracy in generating images, the learning curve of an application and the speed with which the application can generate images.
-With these points of consideration it should be possible to score each application on their ease of use, and on their future potential if the artist were to stick with that application.
+In answering this question, we will consider: the tools available to an artist, the difficulty in using these tools, the accuracy in generating images, the learning curve of an application and the speed with which the application can generate images.
+With these points of consideration, it should be possible to score each application on their ease of use, and on their future potential if the artist were to stick with that application.
 
@@
 	In order to find out which is the best one, we will first look at the accuracy with which the generator can create images.
-We will score the accuracy with an API developed by DeepAI which can calculate image similarity.
+These images will then be scored using an API developed by DeepAI which can calculate image similarity.
 \cite{imageSimilarity}
@@
 
-	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition(see figure 2 below).
+	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition (see figure 2 below).
 	Subject 1 has experience with Midjourney and Subject 2 has experience with Stable diffusion and neither of them have any experience in the other applications.
@@
 		\includegraphics[width=1\linewidth]{OG}
-		\caption{}
+		\caption{The image the subjects tried to replicate}
 		\label{fig:og}
@@
 This way we can see how close each iteration is to the image we are trying to recreate.
-The amount of iterations each application is able to create then gives us insight into how fast the application is and how many iterations you have to do to achieve a certain result.
+The number of iterations each application is able to create then gives us insight into how fast the application is and how many iterations you have to do to achieve a certain result.
 We also gain an idea of how easy to use each application is through this process.
@@
 	In order to compare the image generation applications effectively we observe a multitude of factors that will indicate the strengths and weaknesses of that application.
-These factors are: The amount of iterations each participant can generate while trying to create the image within the 15 minute time limit, how close each iteration is to the image we are trying to replicate using the ai image comparing API's unit of measurement (the unit is called distance.
-The closer to zero the distance is, the closer the images are together.
-Zero means that the two images that are being compared are exactly the same), how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment.
+These factors are: the amount of iterations each subject can generate while trying to create the image within the 15 minute time limit, how easily we were able to access the application and its functionality, how much functionality each application offers and their effects on the final results of our experiment and finally how close each iteration is to the image we are trying to replicate using the ai image comparing API's unit of measurement (the unit is called distance).
+The closer to zero the distance is, the more similar the images are to each other.
+A distance of zero means that the two images that are being compared are exactly the same.
 
@@
 
-	In these graphs the x value is the array of different applications that we use and the y value is the result of that (the distance) for each iteration on the road to trying to recreate an image using these applications.
-The intervening variable in this case would be the amount of experience using these applications.
+	In these graphs the x value is the iteration number for that application and the y value is the result (the distance) for each iteration on the road to trying to recreate an image using these applications.
+This will allow us to compare the timelines of each subject's attempt at recreating the original image and gives us insight into each applications process of text-to-image generation.
+The intervening variable in this case would be the amount of experience each subject has with using these applications.
 
-	We also want to check each applications average result across both Subject 1 and Subject 2 in order to compare how close each iteration gets to the original image on average.
-This will show us if there are any large differences between the applications as a whole.
-If there is this will play a role in choosing which is the best application.
+	We also want to check each applications average result across both Subject 1 and Subject 2 in order to compare how close each application gets to the original image on average.
+This will show us if there are any large differences between the applications as a whole, in terms of the accuracy of the images the applications were able to create.
+If there is, this will play a role in choosing which is the best application.
 
@@
 		\centering
-		\includegraphics[width=1\linewidth]{LineGraphStableDiff}
-		\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphStableDiff}
+		\caption{Line graph showing distance of each iteration for both subjects 1 and 2 for Stable diffusion}
 		\label{fig:linegraphstablediff}
@@
 		\centering
-	\includegraphics[width=1\linewidth]{LineGraphMidJ}
-	\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphMidJ}
+		\caption{Line graph showing distance of each iteration for both subjects 1 and 2 for Midjourney}
 		\label{fig:linegraphmidj}
@@
 
-\subsection{Figure 3 and 4}
+	\subsection{Explaining figure 3 and 4}
 
-What is interesting in both figure one and two is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
-This is seen with Subject two having nearly double the amount of iterations when compared to Subject one in figure 3 and then Subject 1 having more iterations than Subject two in figure 4.
-Another point of interest is that the application in figure one has as a small amount of iterations when compared to the other applications.
+	What is interesting in both figure 3 and 4 is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
+This is seen with subject 2 having nearly double the number of iterations when compared to subject 1 in figure 3 and then subject 1 having more iterations than subject 2 in figure 4.
+Another point of interest is that the application in figure 3 has as a small number of iterations when compared to the other applications.
 	\begin{figure}[!htbp]
 		\centering
-	\includegraphics[width=1\linewidth]{LineGraphDall-E}
-	\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphDall-E}
+		\caption{Line graph showing distance of each iteration for both subjects 1 and 2 for Dall-E}
 		\label{fig:linegraphdall-e}
@@
 		\centering
-	\includegraphics[width=1\linewidth]{LineGraphDBW}
-	\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphDBW}
+		\caption{Line graph showing distance of each iteration for both subjects 1 and 2 for Dream by Wombo}
 		\label{fig:linegraphdbw}
@@
 	\pagebreak
-\subsection{Figure 5 and 6}
+	\subsection{Explaining figure 5 and 6}
 
 	In figure 5 we see that Dall-E has the most iterations out of any of the other applications.
-When comparing the amount of iterations that each subject has in both figure 3 for Stable diffusion and figure 4 for Midjourney, the two applications are very far apart.
-In contrast the amount of iterations between each subject is very close together in figure 5 for Dall-E and figure 6 for Dream by Wombo.
+When comparing the number of iterations that each subject has in both figure 3 for Stable diffusion and figure 4 for Midjourney, the two applications are very far apart.
+In contrast the number of iterations between each subject is very close together in figure 5 for Dall-E and figure 6 for Dream by Wombo.
 
@@
 		\centering
-	\includegraphics[width=1\linewidth]{Bargraph}
-	\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{Bargraph}
+		\caption{Bargraph showing the average distances of all iterations per application for both subjects 1 and 2}
 		\label{fig:bargraph}
 	\end{figure}
-\pagebreak
-\subsection{Figure 7}
-Figure 5 shows that the average distances of all the applications from both subjects one and two are very close.
+
+	\subsection{Explaining figure 7}
+	Figure 7 shows that the average distances of all the applications from both subjects 1 and 2 are very close.
 When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.
@@
 		\centering
-		\includegraphics[width=1\linewidth]{boxplotWithAllData}
-		\caption{}
+		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{boxplotWithAllData}
+		\caption{Boxplot showing range of combined distances for both subjects 1 and 2 per application}
 		\label{fig:boxplotwithalldata}
@@
 	\pagebreak
-\subsection{Figure 8}
+	\subsection{Explaining figure 8}
 
 	In Figure 8 there are two important points of interest.
-Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between quartile 2 and quartile 3.
+Firstly, is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications, as well as having the largest interquartile range.
 This means the spread of the distances is also the largest out of any of the other applications.
@@
 	In order to find the best application out of the four we chose we needed to see what actually makes a text-to-image generation application good.
-This was done by a analysing figures 3 through to 7.
-The applications shown in figure 3 and 4 are applications that both subjects have experience in (Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion).
-What makes figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate because the quality of the images is very random which can be seen with how the line graphs from figures 3 to 6 all fluctuate hugely and never set any kind of discernible pattern.
+This was done by an analysing figures 3 through 7.
+The applications shown in figures 3 and 4 are applications that both subjects have experience in (subject 1 has experience with Midjouney and subject 2 has experience with Stable diffusion).
+What makes figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the number of iterations the user is able to generate.
 
-	In figure 5 and 6 we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in.
-using comparative analysis we can then compare both the graphs that the users have experience in (being figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.
+	In figure 5 and 6 we then see two applications that neither subject 1 nor subject 2 have any prior experience in.
+Using comparative analysis we can then compare both the graphs that the users have experience in (being figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.
 
-	When we take a look at figure 7 we can see that even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars is very small.
+	When we take a look at figure 7, we can see that even though it is the combinations of the averages of all iterations across both subject 1 and 2 per application, the differences between the bars is very small.
 This can be attributed to the nature of text-to-image generation being that of a random series of attempts until the user reaches a point where they are happy with the result.
-This is further proven when you look at any of the patterns for figures 3 through 6 and how the distance for each application's iterations follow no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
-An example of this can be seen in figure 4 with Subject 1.
+This is further proven when you look at any of the patterns for figures 3 through 6 and how the distance for each application's iterations follows no discernible pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
+An example of this can be seen in figure 4 with subject 1.
+
+	Finally in figure 8 we see the spreads of each of the applications.
+This is important as when generating an image using a text-to-image generation application, the user relies a lot on randomness and luck.
+Thus, having a larger spread can actually be a good thing because the more spread you have the more varied your results will be which means while you may get worse results sometimes it also means that you may get better results.
 
@@
 
-	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of generated images with inexperienced users which makes sense as they may struggle to use said functionality.This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.
-	We also looked at how easy the application was to gain access to and came to the conclusion that every one of them was very easy to use and gain access to, so that also became an irrelevant comparison factor.
+	In order to answer the secondary research question, we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of generated images with inexperienced users which makes sense as they may struggle to use said functionality in the first place.
+This can be seen when you take into consideration that stable diffusion has the most functionality but has the worst average iteration quality across both users.
+	We also looked at how easy the application was to gain access to and came to the conclusion that every one of them was very easy to use and gain access to as they were all just on websites, so that also became an irrelevant comparison factor.
+	The accuracy of each of the applications also became less relevant as they were very close to each other, however this doesn't mean that factors relating to accuracy are no longer relevant.
+This can be seen with the spread of the distances, because in text-to-image generation the user will benefit from more varied results and thus an application that can supply that is usually better for an inexperienced user.
+	In terms of looking at learning curve when judging an application for an inexperienced learner this also became less relevant.
+We came to this conclusion after looking at figure 3 to 5 (line graphs) and noticing that having experience doesn't seem to impact image quality but rather just how many images you are able to create.
 
-	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generation technique is nor is it about how much functionality it supplies it's user.
+	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generation technique is nor is it about how much functionality it supplies its user.
 This is because AI text-to-image generation is very random and relies a lot on luck with our current technology even for users that are experienced with these applications.
-What we do know is that currently if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make, the faster you are more likely to get the result you are looking for.
+What we do know is that currently if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make, the faster you are more likely to get the result you are looking for provided the spread of the results is large enough.
 
@@
 With this in mind we can then say that the best application out of the four we chose is Dall-E as it is able to generate the most iterations.
-On a side note our experience with it also lead to us believing that it offers a very streamline user experience, is easy to access and intuitive to use.
+On a side note, our experience with it also led to us believing that it offers a very streamline user experience, is easy to access and intuitive to use.
+Finally, it also provides the most spread out of any of the applications.
 
@@
 	Secondly you can use many different ways to compare images rather than just one in order to make the results more accurate.
-This can be done with surveys where you ask people which image is closer to a humans perspective or by using not just one application for image comparison.
+This can be done with surveys where you ask people which image is closer to a human’s perspective or by using not just one application for image comparison.
 

### 2023-01-25 Paper.tex
commit

@@
 	\subsection{Context and background}
-	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators, an artificial intelligence technique that translates human text into a computer-generated image.
+	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators.
+"With text-to-image models, people provide a text description and the models produce images matching the description as closely as possible" (\cite{whatIsTextToImageGen}).
 You will likely have heard of at least one of these if you frequent the internet.
-This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image), but it has also made the landscape more difficult to navigate because of its abundance of choice.
-This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process.
+This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image).
+However, in our opinion it has also made the landscape more difficult to navigate because of its abundance of choice.
+This is illustrated by this article which shows that you would have to go through all of the models to find which is the best for each user as this author and most others all base their judgment on their own opinion (\cite{whyUseImageComp}).
+This paper makes an effort to try and alleviate this problem by picking four of the most used text-to-image generators and comparing them based on their accuracy and process in an objective way.
 This allows us to help people gain some perspective on which text-to-image generator is best for their needs.
 
-	A research paper was published on the nineteenth of February 2020 called: "A survey and taxonomy of adversarial neural networks for text-to-image synthesis", \cite{agnese2020survey} that makes use of surveys to compare models for text-to-image generations.
+	A research paper was published that makes use of surveys to compare models for text-to-image generations (\cite{agnese2020survey}).
 This paper aimed to show which text-to-image technique yielded the most realistic results in a wide variety of categories.
@@
 	The text-to-image generators we will be testing during the course of this paper are: Stable diffusion, Midjourney, DallE and Dream by Wombo.
-We came to these models after looking at several applications in Google Trends.
-\cite{googleTrends} This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
+We came to these models after looking at several applications in Google Trends (\cite{googleTrends}).
+This gave us a good idea of what the landscape looked like, and which applications artists would be likely to choose.
 You may notice below in Figure 1 that Dream by Wombo is not that popular anymore, however it was one of the first openly accessible text-to-image applications out there.
@@
 	\end{figure}
-
-	\pagebreak
 
@@
 	In order to find out which is the best one, we will first look at the accuracy with which the generator can create images.
-These images will then be scored using an API developed by DeepAI which can calculate image similarity.
-\cite{imageSimilarity}
+These images will then be scored using an API developed by DeepAI which can calculate image similarity (\cite{imageSimilarity}).
 
@@
 
-	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition (see figure 2 below).
+	We have chosen an image that we find sufficiently covers all the challenging parts of recreating an image using ai art generation such as reflections and complex composition (see Figure 2 below).
 	Subject 1 has experience with Midjourney and Subject 2 has experience with Stable diffusion and neither of them have any experience in the other applications.
@@
 	\subsubsection{Scoring generated images}
-	With those sets of data, we then plug the images (each iteration) into the image similarity checking API, \cite{imageSimilarity}, that can give you a numerical value for how close one image is to another.
+	With those sets of data, we then plug the images (each iteration) into the image similarity checking API that can give you a numerical value for how close one image is to another (\cite{imageSimilarity}).
 This way we can see how close each iteration is to the image we are trying to recreate.
@@
 
+	We make use of 4 different web applications in order to get our results that are presented below.
+Firstly, Stable diffusion which is an open source text-to-image generator and offers a lot of functionality (\cite{stableDiff}).
+Second, Dall-E has a great ease of use, especially for how good the generated images look (\cite{dallE}).
+Third, Midjourney is the most popular out of our selection and is very similar to Dall-E in our opinion (\cite{midjourney}).
+Finally, Dream by Wombo is the last application and is the oldest out of the applications we are looking at (\cite{dreamByWombo}).
+
 	\begin{figure}[!!htbp]
 		\centering
+		\bfseries
+		\title{Stable diffusion}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphStableDiff}
@@
 		\centering
+		\bfseries
+		\title{Midjourney}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphMidJ}
@@
 
-	\subsection{Explaining figure 3 and 4}
+	\subsection{Explaining Figure 3 and 4}
 
-	What is interesting in both figure 3 and 4 is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
-This is seen with subject 2 having nearly double the number of iterations when compared to subject 1 in figure 3 and then subject 1 having more iterations than subject 2 in figure 4.
-Another point of interest is that the application in figure 3 has as a small number of iterations when compared to the other applications.
+	What is interesting in both Figure 3 and 4 is that the discrepancy between the two subjects in both applications is larger than that of any of the other applications we tested.
+This is seen with subject 2 having nearly double the number of iterations when compared to subject 1 in Figure 3 and then subject 1 having more iterations than subject 2 in Figure 4.
+Another point of interest is that the application in Figure 3 has as a small number of iterations when compared to the other applications.
 	\begin{figure}[!htbp]
 		\centering
+		\bfseries
+		\title{Dall-E}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphDall-E}
@@
 		\centering
+		\bfseries
+		\title{Dream by Wombo}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{LineGraphDBW}
@@
 	\pagebreak
-	\subsection{Explaining figure 5 and 6}
+	\subsection{Explaining Figure 5 and 6}
 
-	In figure 5 we see that Dall-E has the most iterations out of any of the other applications.
-When comparing the number of iterations that each subject has in both figure 3 for Stable diffusion and figure 4 for Midjourney, the two applications are very far apart.
-In contrast the number of iterations between each subject is very close together in figure 5 for Dall-E and figure 6 for Dream by Wombo.
+	In Figure 5 we see that Dall-E has the most iterations out of any of the other applications.
+When comparing the number of iterations that each subject has in both Figure 3 for Stable diffusion and Figure 4 for Midjourney, the two applications are very far apart.
+In contrast the number of iterations between each subject is very close together in Figure 5 for Dall-E and Figure 6 for Dream by Wombo.
 
@@
 		\centering
+		\bfseries
+		\title{Average distances}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{Bargraph}
@@
 
-	\subsection{Explaining figure 7}
+	\subsection{Explaining Figure 7}
 	Figure 7 shows that the average distances of all the applications from both subjects 1 and 2 are very close.
@@
 		\centering
+		\bfseries
+		\title{Range of combined distances}
 		\includegraphics[width=1\linewidth, trim=0 0 0 50, clip]{boxplotWithAllData}
@@
 	In order to find the best application out of the four we chose we needed to see what actually makes a text-to-image generation application good.
-This was done by an analysing figures 3 through 7.
-The applications shown in figures 3 and 4 are applications that both subjects have experience in (subject 1 has experience with Midjouney and subject 2 has experience with Stable diffusion).
-What makes figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the number of iterations the user is able to generate.
+This was done by an analysing Figures 3 through 7.
+The applications shown in Figures 3 and 4 are applications that both subjects have experience in (subject 1 has experience with Midjouney and subject 2 has experience with Stable diffusion).
+What makes Figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the number of iterations the user is able to generate.
 
-	In figure 5 and 6 we then see two applications that neither subject 1 nor subject 2 have any prior experience in.
-Using comparative analysis we can then compare both the graphs that the users have experience in (being figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.
+	In Figure 5 and 6 we then see two applications that neither subject 1 nor subject 2 have any prior experience in.
+Using comparative analysis we can then compare both the graphs that the users have experience in (being Figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being Figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.
 
-	When we take a look at figure 7, we can see that even though it is the combinations of the averages of all iterations across both subject 1 and 2 per application, the differences between the bars is very small.
+	When we take a look at Figure 7, we can see that even though it is the combinations of the averages of all iterations across both subject 1 and 2 per application, the differences between the bars is very small.
 This can be attributed to the nature of text-to-image generation being that of a random series of attempts until the user reaches a point where they are happy with the result.
-This is further proven when you look at any of the patterns for figures 3 through 6 and how the distance for each application's iterations follows no discernible pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
-An example of this can be seen in figure 4 with subject 1.
+This is further proven when you look at any of the patterns for Figures 3 through 6 and how the distance for each application's iterations follows no discernible pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.
+An example of this can be seen in Figure 4 with subject 1.
 
-	Finally in figure 8 we see the spreads of each of the applications.
+	Finally in Figure 8 we see the spreads of each of the applications.
 This is important as when generating an image using a text-to-image generation application, the user relies a lot on randomness and luck.
@@
 	In terms of looking at learning curve when judging an application for an inexperienced learner this also became less relevant.
-We came to this conclusion after looking at figure 3 to 5 (line graphs) and noticing that having experience doesn't seem to impact image quality but rather just how many images you are able to create.
+We came to this conclusion after looking at Figure 3 to 5 (line graphs) and noticing that having experience doesn't seem to impact image quality but rather just how many images you are able to create.
 

### 2023-01-26 Paper.tex
Commit

@@
 	\begin{abstract}
-		Following the explosion of artificial intelligence during the year of 2022, there are now many text-to-image generation applications out there.
+		Following the increase in popularity of artificial intelligence during the year of 2022, there are now many text-to-image generation applications out there.
 This is great for the field of artificial intelligence as a whole, however it has made knowing which application is best quite hard for artists who are new to text-to-image generation.
@@
 	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators.
-"With text-to-image models, people provide a text description and the models produce images matching the description as closely as possible" (\cite{whatIsTextToImageGen}).
-You will likely have heard of at least one of these if you frequent the internet.
-This explosion in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image).
+According to \citeauthor{whatIsTextToImageGen} (\citeyear{whatIsTextToImageGen}), text-to-image generators allow people to provide a text description which the generator then uses to produce images matching the description as closely as possible.
+This increase in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image).
 However, in our opinion it has also made the landscape more difficult to navigate because of its abundance of choice.
@@
 	We expect the best text-to-image generator out of the four we chose to be stable diffusion.
-This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting (allows you to regenerate a specific area of an image without regenerating the whole image), this allows the user more freedom to fine-tune their result.
+This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting.
+According to \citeauthor{inpaintingExplaination} (\citeyear{inpaintingExplaination}), inpainting is an AI technique which allows a user to regenerate a missing part of an image.
+This allows the user more freedom to fine-tune their result.
 Given enough time this will yield a more accurate result.
@@
 		\includegraphics[width=1\linewidth]{OG}
-		\caption{The image the subjects tried to replicate}
+		\caption{The image the subjects tried to replicate (\cite{targetImage})}
 		\label{fig:og}
@@
 	\subsubsection{Scoring generated images}
-	With those sets of data, we then plug the images (each iteration) into the image similarity checking API that can give you a numerical value for how close one image is to another (\cite{imageSimilarity}).
+	We then run the set of generated images, together with the target image through an image similarity checking API that can give you a numerical value for how close one image is to another (\cite{imageSimilarity}).
 This way we can see how close each iteration is to the image we are trying to recreate.
+It is able to score the images based on a color histogram and colour location, this is supposed to be resistant to transformations such as scaling and changes in lighting (\cite{imageSimilarityPaper}).
 The number of iterations each application is able to create then gives us insight into how fast the application is and how many iterations you have to do to achieve a certain result.

### 2023-01-27 Paper.tex
Final changes

@@
 	During the year of 2022 there has been a massive increase in the popularity and use of text-to-image generators.
-According to \citeauthor{whatIsTextToImageGen} (\citeyear{whatIsTextToImageGen}), text-to-image generators allow people to provide a text description which the generator then uses to produce images matching the description as closely as possible.
+Text-to-image generators allow people to provide a text description which the generator then uses to produce images matching the description as closely as possible (\cite{whatIsTextToImageGen}).
 This increase in popularity has led to many different text-to-image applications being made, which on the one hand has given many more options to artists (people who use a text-to-image generator to create and refine an image).
@@
 This is due to the fact that stable diffusion offers its users more tools and techniques like inpainting.
-According to \citeauthor{inpaintingExplaination} (\citeyear{inpaintingExplaination}), inpainting is an AI technique which allows a user to regenerate a missing part of an image.
+Inpainting is an AI technique which allows a user to regenerate a missing part of an image (\cite{inpaintingExplaination}).
 This allows the user more freedom to fine-tune their result.
